---
title: "Visual Cognition Lab"
author: "Andrea Ovalle"
date: "August 25, 2017"
output: html_document
---


#VCA LAB


```{r, message=FALSE, warning=FALSE, include=FALSE}

load("~/Dropbox (HSPH)/VCA LAB/Seque_Data.rda")
require(dplyr)
require(tidyr)
require(ggplot2)
require(plotly) # Interactive graphing 
library(stringr)
library(bsselectR)
library(tidyverse)
library(scales)
library(acs14lite)

multiplot <- function(..., plotlist = NULL, file, cols = 1, layout = NULL) {
  require(grid)

  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  if (is.null(layout)) {
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

  if (numPlots == 1) {
    print(plots[[1]])

  } else {
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    for (i in 1:numPlots) {
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

Seque_Data_1 <- Seque_Data %>% select(TRIAL_LABEL,CURRENT_FIX_INDEX,CURRENT_FIX_INTEREST_AREAS,NEXT_FIX_NEAREST_INTEREST_AREA, RECORDING_SESSION_LABEL,trial,TRIAL_FIXATION_TOTAL) ## This code selects the columns that I am most interested in.
colnames(Seque_Data_1)[colnames(Seque_Data_1)=="RECORDING_SESSION_LABEL"]<-"Subject" # changes the name of x column.

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Num_df_trial <- Seque_Data_1 %>%
  select(Subject, trial)%>%
  group_by(Subject, trial)%>%
  summarise(Total_per_trial = n())%>%
  arrange(desc(Subject))
head(Num_df_trial)

m<-ggplot(Num_df_trial, aes(x = trial, y = Total_per_trial, color= Subject))+ geom_point() + theme(axis.title.y = element_text(size = rel(1.5)))+theme(axis.title.x = element_text(size = rel(1.5)))+theme(legend.key = element_rect(size = rel(1.5)))+theme(axis.text = element_text(size = 15))

ggplotly(m)

```

EXPERIMENT 1A
- Dual target 1-step and 4-step color separations 
- Split- target cost; similarity of targets decreases, fixations to dissimilar distractors increases. ( STROUD DISSERTATIONS EXP 1A)
```{r 1a Present, message=FALSE, warning=FALSE, include=FALSE}

data10 <- read.csv("~/Dropbox/VCA LAB/1a  .Means.TargetPresent.csv")

Data10 <- data10[,-(0:1)] # Substracts columns from the data frame

colnames(Data10) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17","18") # adds labels to columns

df4.9 <- gather(Data10, Length, Prob)%>%na.omit() # arranges data into a long format. 

df5.9 <- transform(df4.9, Sequence=ave(seq_along(Length),Length, FUN=seq_along)) ## Creates a sequence that runs along the lenght of the fixation.

### Adds counts of the trials 

df1.8 <- data.frame(x=c(0:18)) ## adds symbols to each data point for each trial.


my_plot10 <- ggplot(df5.9, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.9$Length, color = Length))+
  geom_point(aes(alpha = 0.03))
  
  
```

```{r 1a Absent, message=FALSE, warning=FALSE, include=FALSE}
data11 <- read.csv("~/Dropbox/VCA LAB/1a  .Means.TargetAbsent.csv")

Data11 <- data11[,-(0:1)] 

colnames(Data11) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17","18")

df5.1 <- gather(Data11, length, Prob)%>%na.omit() # arranges data into a long format. 

df6 <- transform(df5.1, Sequence=ave(seq_along(length), length, FUN=seq_along)) ### Adds counts of the trials 

df1.9 <- data.frame(x=c(0:17)) ## adds symbols to each data point for each trial.

#df6$length <- as.numeric(as.character(df6$length))

my_plot11 <- ggplot(df6, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df6$length, color = length))+
  geom_point(aes(alpha = 0.03))

```

```{r multiplot 1a, echo=FALSE, message=FALSE, warning=FALSE}

list6 <- list()

for (i in 1:2) {
  my_plot11 <- ggplot(df6, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df6$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "1a Absent")
  list6[[1]] <- my_plot11
  

my_plot10 <- ggplot(df5.9, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.9$Length, color = Length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "1a Present")+ylim(0,30) 
list6[[2]] <- my_plot10
  

}

multiplot(plotlist = list6, cols= 2)

```

```{r 1b Present, echo=FALSE, message=FALSE, warning=FALSE}

### (exp. 1b) colour T search

data12 <- read.csv("~/Dropbox/VCA LAB/1b  .Means.TargetPresent.csv")

Data12 <- data12[,-(0:1)] 

colnames(Data12) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17","18")

df5.2 <- gather(Data12, length, Prob)%>%na.omit() # arranges data into a long format. 

df7 <- transform(df5.2, Sequence=ave(seq_along(length), length, FUN=seq_along)) ### Adds counts of the trials 

#df_2 <- data.frame(x=c(0:17)) ## adds symbols to each data point for each trial.



my_plot12 <- ggplot(df7, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df7$length, color = length))+
  geom_point(aes(alpha = 0.03)) # change labs to upper limits 40 for all of them 
```

```{r 1b Absent, echo=FALSE, message=FALSE, warning=FALSE}

data13 <- read.csv("~/Dropbox/VCA LAB/1b  .Means.TargetAbsent.csv")

Data13 <- data13[,-(0:1)] 

colnames(Data13) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17")

df5.3 <- gather(Data13, length, Prob)%>%na.omit() # arranges data into a long format. 

df8 <- transform(df5.3, Sequence=ave(seq_along(length), length, FUN=seq_along)) ### Adds counts of the trials 

#df_3 <- data.frame(x=c(0:17)) ## adds symbols to each data point for each trial.



my_plot13 <- ggplot(df8, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df8$length, color = length))+
  geom_point(aes(alpha = 0.03))


```

```{r multiplot 1b, echo=FALSE, message=FALSE, warning=FALSE}
list7<- list()

for (i in 1:2){
 my_plot12 <- ggplot(df7, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df7$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = " Exp 1b Target Present")+ylim(0,30)
  list7[[1]] <- my_plot12 
  

my_plot13 <- ggplot(df8, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df8$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = " Exp 1b Target Absent")+ylim(0,30)
  list7[[2]] <- my_plot13
}

multiplot(plotlist = list7, cols =2)

```




Color T search plust WM (orientation)

Orientation bar - WM

Color selectivity was unaffected in the search task. WM accuracy as poor (error rate ~35%)
```{r sub 10 Target Absent, echo=FALSE, message=FALSE, warning=FALSE}

data <- read.csv("~/Dropbox/VCA LAB/10  .Means.TargetAbsent.csv") 

Data <- data[,-(0:1)] 

colnames(Data) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17","18")

my_df4 <- gather(Data, length, Prob)%>%na.omit() # arranges data into a long format. 

my_df5 <- transform(my_df4, Sequence=ave(seq_along(length), length, FUN=seq_along)) ### Adds counts of the trials 

my_plot1 <- ggplot(my_df5, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = my_df5$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 10 Target Absent") 



```

```{r Sub 10 Target Present, echo=FALSE, message=FALSE, warning=FALSE}


data2 <- read.csv("~/Dropbox/VCA LAB/10  .Means.TargetPresent.csv")
Data2 <- data2[,-(0:1)] 

colnames(Data2) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17", "18")

df4 <- gather(Data2, length, Prob)%>%na.omit() # arranges data into a long format. 

df5 <- transform(df4, Sequence=ave(seq_along(length), length, FUN=seq_along)) ### Adds counts of the trials 

#df1 <- data.frame(x=c(0:17)) ## adds symbols to each data point for each trial.


my_plot2 <- ggplot(df5, aes(x = Sequence, y = Prob))+
  geom_line(aes(group = df5$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 10 Target Present") 

```

```{r Exp 10 multiplot, echo=FALSE, message=FALSE, warning=FALSE}
list8 <- list()

for(i in 1:2) {
my_plot1 <- ggplot(my_df5, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = my_df5$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle("Exp 10 Target Absent")
list8[[1]]<- my_plot1

 my_plot2 <- ggplot(df5, aes(x = Sequence, y = Prob))+
  geom_line(aes(group = df5$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 10 Target Present")
list8[[2]] <- my_plot2

}

multiplot(plotlist = list8, cols = 2)


```





COLOR T SEARCH PLUS WM ( DOTS )

Spatial dot task. 
Color selectivity was unaffected. WM accuracy was similar to color patch ( error rate ~ 35%)

```{r Exp 11 Absent, echo=FALSE, message=FALSE, warning=FALSE}


data3 <- read.csv("~/Dropbox/VCA LAB/11  .Means.TargetAbsent.csv")

Data3 <- data3[,-(0:1)]  

colnames(Data3) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17","18")

df4.2 <- gather(Data3, length, Prob)%>%na.omit() # arranges data into a long format. 

df5.2 <- transform(df4.2, Sequence=ave(seq_along(length), length, FUN=seq_along)) ### Adds counts of the trials 

#df1.1 <- data.frame(x=c(0:17)) ## adds symbols to each data point for each trial.


my_plot3 <- ggplot(df5.2, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.2$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 11 Target Absent") 

```

```{r sub 11 Present, echo=FALSE, message=FALSE, warning=FALSE}

data4 <- read.csv("~/Dropbox/VCA LAB/11  .Means.TargetPresent.csv")

Data4 <- data4[,-(0:1)]  

colnames(Data4) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17","18")

df4.3 <- gather(Data4, length, Prob)%>%na.omit() # arranges data into a long format. 

df5.3 <- transform(df4.3, Sequence=ave(seq_along(length), length, FUN=seq_along)) ### Adds counts of the trials 

#df1.2 <- data.frame(x=c(0:17)) ## adds symbols to each data point for each trial.

my_plot4 <- ggplot(df5.3, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.3$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 11 Target Present") 
```

```{r multipplot exp 11, echo=FALSE, message=FALSE, warning=FALSE}

list9 <- list()

for (i in 1:2) {
  my_plot3 <- ggplot(df5.2, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.2$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 11 Target Absent")
list9[[1]]<- my_plot3

my_plot4 <- ggplot(df5.3, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.3$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 11 Target Present")
list9[[2]] <- my_plot4
  
}

multiplot(plotlist = list9, cols = 2)

```





COLOR SEARCH AMONG T's plus WM 

Pure color T search with Working memory load. 

```{r sub 12 Absent, echo=FALSE, message=FALSE, warning=FALSE}

##Pure Color T Search with WM (exp. 12)    colour search among T's plus WM

data5 <- read.csv("~/Dropbox/VCA LAB/12 .Means.TargetAbsent.csv")

Data5 <- data5[,-(0:1)]  

colnames(Data5) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17","18")

df4.4 <- gather(Data5, length, Prob)%>%na.omit() # arranges data into a long format. 

df5.4 <- transform(df4.4, Sequence=ave(seq_along(length), length, FUN=seq_along)) ### Adds counts of the trials 

my_plot5 <- ggplot(df5.4, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.4$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 12 Target Absent") 
```

```{r sub 12 Present, echo=FALSE, message=FALSE, warning=FALSE}
data6 <- read.csv("~/Dropbox/VCA LAB/12 .Means.TargetPresent.csv")

Data6 <- data6[,-(0:1)]  

colnames(Data6) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17")

df4.5 <- gather(Data6, length, Prob)%>%na.omit() # arranges data into a long format. 

df5.5 <- transform(df4.5, Sequence=ave(seq_along(length), length, FUN=seq_along)) ### Adds counts of the trials 

#df1.4 <- data.frame(x=c(0:17)) ## adds symbols to each data point for each trial.



my_plot6 <- ggplot(df5.5, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.5$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 12 Target Present") 

```

```{r multiplot exp 12, echo=FALSE, message=FALSE, warning=FALSE}

list10 <- list()

for (i in 1:2){
  my_plot5 <- ggplot(df5.4, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.4$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 12 Target Absent")
  list10[[1]]<-my_plot5
  
  my_plot6 <- ggplot(df5.5, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.5$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 12 Target Present")
  list10[[2]]<- my_plot6
}

multiplot(plotlist = list10, cols = 2)

```





Color Search among T's

Single target pure color search similar to Exp 12 but not W, and with a new set of stimuli

```{r exp 16 Absent, echo=FALSE, message=FALSE, warning=FALSE}


##Pure Color T Search No WM (exp. 16)    colour search among T's


data7 <- read.csv("~/Dropbox/VCA LAB/16 .Means.TargetAbsent.csv")

Data7 <- data7[,-(0:1)] 


colnames(Data7) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17","18")


df4.6 <- gather(Data7, length, Prob)%>%na.omit() # arranges data into a long format. 

df5.6 <- transform(df4.6, Sequence=ave(seq_along(length), length, FUN=seq_along)) ### Adds counts of the trials 

#df1.5 <- data.frame(x=c(0:17)) ## adds symbols to each data point for each trial.



my_plot7 <- ggplot(df5.6, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.6$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 16 Absent") 

```

```{r sub 16 Present, echo=FALSE, message=FALSE, warning=FALSE}

data7.1 <- read.csv("~/Dropbox/VCA LAB/16 .Means.TargetPresent.csv")

Data7.1 <- data7.1[,-(0:1)]

colnames(Data7.1) =c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17","18")

df4.6.1 <- gather(Data7.1, length, Prob)%>%na.omit() # arranges data into a long format. 

df5.6.1 <- transform(df4.6.1, Sequence=ave(seq_along(length), length, FUN=seq_along)) ### Adds counts of the trials 

#df1.5.1 <- data.frame(x=c(0:17)) ## adds symbols to each data point for each trial.



my_plot7.1 <- ggplot(df5.6.1, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.6.1$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 16 Present") 

```

```{r multiplot exp 16, echo=FALSE, message=FALSE, warning=FALSE}

List11 <- list()

for (i in 1:2){
  my_plot7 <- ggplot(df5.6, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.6$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 16 Absent")+ylim(0,30)
  List11[[1]]<- my_plot7
  
 my_plot7.1 <- ggplot(df5.6.1, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.6.1$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 16 Present")+ylim(0,30)
 List11[[2]]<- my_plot7.1
}

multiplot(plotlist = List11, cols=2)
```


Dual Target Pure Color T search 
Two color search among T's 
Dual target color search with only T's (4step)
```{r Sub 18 Present, echo=FALSE, message=FALSE, warning=FALSE}

###Dual Target Pure Color Search (4-step) (exp. 18)    dual colour search among T's

data8 <- read.csv("~/Dropbox/VCA LAB/18 .Means.TargetPresent (1).csv")

Data8 <- data8[,-(0:1)] 

colnames(Data8) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17","18")

df4.7 <- gather(Data8, length, Prob)%>%na.omit() # arranges data into a long format. 

df5.7 <- transform(df4.7, Sequence=ave(seq_along(length),length, FUN=seq_along)) ### Adds counts of the trials 

#df1.6 <- data.frame(x=c(0:17)) ## adds symbols to each data point for each trial.

my_plot8 <- ggplot(df5.7, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.7$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 18 Target Present") 
```

```{r Sub 18 Absent, echo=FALSE, message=FALSE, warning=FALSE}
data9 <- read.csv("~/Dropbox/VCA LAB/18 .Means.TargetAbsent.csv")

Data9 <- data9[,-(0:1)] 

colnames(Data9) = c("03","04","06","07","08","09","10","11","12","13","14","15","16","17","18","19")

df4.8 <- gather(Data9, length, Prob)%>%na.omit() # arranges data into a long format. 

df5.8 <- transform(df4.8, Sequence=ave(seq_along(length),length, FUN=seq_along)) ### Adds counts of the trials 

#df1.7 <- data.frame(x=c(0:17)) ## adds symbols to each data point for each trial.



my_plot9 <- ggplot(df5.8, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.8$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 18 Target Absent") 

```

```{r multiplo(t exp 18, echo=FALSE, message=FALSE, warning=FALSE}
list12 <- list()
for (i in 1:2){
  my_plot8 <- ggplot(df5.7, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.7$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 18 Target Present")+ylim(0,30)
  list12[[1]]<- my_plot8
  
my_plot9 <- ggplot(df5.8, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df5.8$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 18 Target Absent")+ylim(0,30)
  list12[[2]]<- my_plot9
  
}
 multiplot(plotlist = list12, cols = 2)

```
    
  
  
  
  
    
    
COLOR T SEARCH PLUS WORKING MEMORY 

- Single target search for color with color patch working memory load
- Color selectivity with the WM load was disrupted across al distractor colors. The identity of the WM load color had no specific effect on the search fixation patterns. 
WM accuracy was okay for exact color ( ~ 35% error rate) but excellent for 1-2 steps from color (~8%)

```{r 7 Present}
data14 <- read.csv("~/Dropbox/VCA LAB/7  .Means.TargetPresent.csv")

Data14 <- data14[,-(0:1)] 

colnames(Data14) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17","18")

df5.4 <- gather(Data14, length, Prob)%>%na.omit() # arranges data into a long format. 

df9 <- transform(df5.4, Sequence=ave(seq_along(length), length, FUN=seq_along)) ### Adds counts of the trials 

#df_4 <- data.frame(x=c(0:17)) ## adds symbols to each data point for each trial.



my_plot14 <- ggplot(df9, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df9$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 7 Target Present")+ylim(0,30)

```

```{r 7 Absent, echo=FALSE, message=FALSE, warning=FALSE}
data15 <- read.csv("~/Dropbox/VCA LAB/7  .Means.TargetAbsent.csv")

Data15 <- data15[,-(0:1)] 

colnames(Data15) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17","18")

df5.5 <- gather(Data15, length, Prob)%>%na.omit() # arranges data into a long format. 

df10 <- transform(df5.5, Sequence=ave(seq_along(length),length, FUN=seq_along)) ### Adds counts of the trials 

#df_5 <- data.frame(x=c(0:17)) ## adds symbols to each data point for each trial.



my_plot15 <- ggplot(df10, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df10$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 7 Target Absent")

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
list13 <- list()

for (i in 1:2){
  my_plot14 <- ggplot(df9, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df9$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 7 Target Present")
  list13[[1]]<- my_plot14
  
  my_plot15 <- ggplot(df10, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df10$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 7 Target Absent")
  list13[[2]]<- my_plot15

}

multiplot(plotlist = list13, cols = 2)

```





COLOR T SEARCH PLUS WORKING MEMORY 

Single target search for color with WM load.

- Color selectivity was slightly affected across all distractor colors. Working memory accuracy was very good (~10% error rate)
```{r 8 Present, echo=FALSE, message=FALSE, warning=FALSE}

data16 <- read.csv("~/Dropbox/VCA LAB/8  .Means.TargetPresent.csv")

Data16 <- data16[,-(0:1)] 

colnames(Data16) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17")

df5.6 <- gather(Data16, length, Prob)%>%na.omit() # arranges data into a long format. 

df11 <- transform(df5.6, Sequence=ave(seq_along(length),length, FUN=seq_along)) ### Adds counts of the trials 

#df_6 <- data.frame(x=c(0:17)) ## adds symbols to each data point for each trial.



my_plot16 <- ggplot(df11, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df11$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 8 Target Present")
```


```{r 8 Absent, echo=FALSE, message=FALSE, warning=FALSE}

data17 <- read.csv("~/Dropbox/VCA LAB/8  .Means.TargetAbsent.csv")


Data17 <- data17[,-(0:1)] 

colnames(Data17) = c("03","04","05","06","07","08","09","10","11","12","13","14","15","16","17")

df5.7 <- gather(Data17, length, Prob)%>%na.omit() # arranges data into a long format. 

df12 <- transform(df5.7, Sequence=ave(seq_along(length), length, FUN=seq_along)) ### Adds counts of the trials 

##df_7 <- data.frame(x=c(0:17)) ## adds symbols to each data point for each trial.



my_plot17 <- ggplot(df12, aes(x = Sequence , y =Prob))+
  geom_line(aes(group = df12$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "")
```


```{r multiplot exp 8, echo=FALSE, message=FALSE, warning=FALSE}

list14 <- list()

for (i in 1:2){
  my_plot16 <- ggplot(df11, aes(x = Sequence , y = Prob))+
  geom_line(aes(group = df11$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 8 Target Present")+ylim(0,30)
  list14[[1]]<- my_plot16
 
  
  my_plot17 <- ggplot(df12, aes(x = Sequence , y =Prob))+
  geom_line(aes(group = df12$length, color = length))+
  geom_point(aes(alpha = 0.03))+ggtitle(label = "Exp 8 Target Absent")+ylim(0,30) 
  list14[[2]]<- my_plot17

  }


multiplot(plotlist = list14, cols =2)


```


